\thetitle

### 2021-05-25 writing/paper.tex
turn of Acknws so we don't forget
Add Robby and NWU PLT to acknowledgements

%% Acknowledgments
\begin{acks}                 
Felleisen and Greenman were partly supported by NSF grants SHF
1763922. Greenman also received support from a CRA-NSF Post-doctoral
fellowship grant. Dimoulas and Felleisen wish to thank Max New for
extensive discussions of the early ides in this paper. 
\end{acks}

>>>>

%% Acknowledgments
\begin{acks}                 
Felleisen and Greenman were partly supported by NSF grant SHF
1763922. Greenman also received support from a CRA-NSF Post-doctoral
fellowship grant. Dimoulas and Felleisen wish to thank Max New for
extensive discussions of the early ideas in this paper. Thanks also to
Robby Findler and Northwestern PLT for their valuable feedback at
various stages of this work.
\end{acks}
